---
title: "Anonymized Graphics Table"
output: html_notebook
---
#Uses Deidentified Patient Data# 

#Load Required Packages
```{r}
#Load Required Packages# 
library(dplyr)
library(tidyr)
library(reshape2)
```

#Set WD 
```{r}
rm(list=ls())
setwd("~/Box Sync/Residency/Research/OPTIMAL Data Analysis/Analysis 2022/")
```

#Read in Data
```{r}
COVID_Data <- read.table("~/Box Sync/Residency/Research/OPTIMAL Data Analysis/Analysis 2022/Input_COVIDAdmissions_Anonymized.csv", sep=",", header=T)

#Add A Column for OPTIMAL
COVID_Data$OPTIMAL <- ifelse(is.na(COVID_Data$Clinic_Visit_Date)==TRUE,0,1)

#Convert Dates to Dates
COVID_Data$Admission_Date <- as.Date(COVID_Data$Admission_Date, format='%m/%d/%Y')
COVID_Data$Discharge_Date <- as.Date(COVID_Data$Discharge_Date, format='%m/%d/%Y')
COVID_Data$Clinic_Visit_Date <- as.Date(COVID_Data$Clinic_Visit_Date, format='%m/%d/%Y')

```

#Subset by OPTIMAL
```{r}
OPTIMAL <- subset(COVID_Data,COVID_Data$OPTIMAL==1)
Not_OPTIMAL <- subset(COVID_Data,COVID_Data$OPTIMAL==0)
```

#Separate Catagorical and Continuous Data
```{r}
colnames(COVID_Data)
ALL_Cont <- COVID_Data[,c(1,22,5,6,7,8,20)]
ALL_Cat <- COVID_Data[,c(1,22,9:13,15:19,21)]
```

#For Continuous Data make a Table that Contains the Following
- Median
- iQR
- p Value (Wilcoxan)
Summarize for the Following Groups
- OPTIMAL
- Not OPTIMAL

#Analysis of Continuous Data
#Summarize Entire Cohort
```{r}
Input <- ALL_Cont

#Create a Table for Continuous Data
Summary <- matrix(data=NA, nrow=13, ncol=5,dimnames=list(c("Cohort-Median","Cohort-SD","Cohort-IQRLow","Cohort-IQRHigh","OPTIMAL-Median","OPTIMAL-SD","OPTIMAL-IQRLow","OPTIMAL-IQRHigh","NotOPTIMAL-Median","NotOPTIMAL-SD","NotOPTIMAL-IQRLow","NotOPTIMAL-IQRHigh","p-value"),c(1:5)))

#Summarize Data for Whole Cohort
RiskFactors <- names(Input[,c(3:7)])

for (i in 1:5){
  var <- RiskFactors[i]
  Summary[1,(i)] <- median(Input[,var],na.rm=TRUE)
  Summary[2,(i)] <- sd(Input[,var],na.rm=TRUE)
  Summary[3,(i)] <- mean(Input[,var],na.rm=TRUE) - .675*sd(Input[,var],na.rm=TRUE)
  Summary[4,(i)] <- mean(Input[,var],na.rm=TRUE) + .675*sd(Input[,var],na.rm=TRUE)
  colnames(Summary) <- paste0(RiskFactors,".Summary")
}   
```

#Summarize Continuous Data for OPTIMAL
```{r}
Input<-OPTIMAL

for (i in 1:5){
  var<-RiskFactors[i]
  Summary[5,(i)] <- median(Input[,var],na.rm=TRUE)
  Summary[6,(i)] <- sd(Input[,var],na.rm=TRUE)
  Summary[7,(i)] <- mean(Input[,var],na.rm=TRUE) - .675*sd(Input[,var],na.rm=TRUE)
  Summary[8,(i)] <- mean(Input[,var],na.rm=TRUE) + .675*sd(Input[,var],na.rm=TRUE)
}
```

#Summarize Continuous Data for NotOPTIMAL
```{r}
Input<-Not_OPTIMAL

for (i in 1:5){
  var<-RiskFactors[i]
  Summary[9,(i)] <- median(Input[,var],na.rm=TRUE)
  Summary[10,(i)] <- sd(Input[,var],na.rm=TRUE)
  Summary[11,(i)] <- mean(Input[,var],na.rm=TRUE) - .675*sd(Input[,var],na.rm=TRUE)
  Summary[12,(i)] <- mean(Input[,var],na.rm=TRUE) + .675*sd(Input[,var],na.rm=TRUE)
}
```

#Compare Continuous for OPTIMAL and Not_OPTIMAL with Wilcox Test
```{r}
Input <- ALL_Cont

for (i in 1:5){
  var<-RiskFactors[i]
  OPTIMAL_RiskFactor_p<-pairwise.wilcox.test(Input[,var],Input$OPTIMAL,pool.sd=T,paired=F,alternative="two.sided")
  Summary[13,(i)]<-as.numeric(OPTIMAL_RiskFactor_p$p.value)
}
Summary

pairwise.wilcox.test(Input$Age_years,Input$OP)
```

#Make an Output Table for the Continuous Data
```{r}
Output <- t(Summary)
write.table(Output, file="ALL_Cont_ByOptimal.txt", sep="\t", quote=F, row.names=T)
```

#For Catagorical Data make a Table that Contains the following:
- Number
- %
- P value (Fisher)
Summarize for the Following Groups
- OPTIMAL
- Not OPTIMAL

#Analysis of Catagorical Data
#Summarize Entire Cohort
```{r}
Input <- ALL_Cat

#Create a Table for Continuous Data
Summary <- matrix(data=NA, nrow=7, ncol=5,dimnames=list(c("Cohort-N","Cohort-Percent","OPTIMAL-N","OPTIMAL-Percent","NotOPTIMAL-N","NotOPTIMAL-Percent","p-value"),c(1:5)))

#Summarize Data for Whole Cohort
RiskFactors <- names(Input[,c(8:12)])

for (i in 1:5){
  var <- RiskFactors[i]
  Summary[1,(i)] <- sum(Input[,var])
  Summary[2,(i)] <- 100*sum(Input[,var])/length(Input[,var])  
  colnames(Summary) <- paste0(RiskFactors,".Summary")
}   
```

#Analysis of Catagorical Data
#Summarize OPTIMAL
```{r}
Input <- OPTIMAL

for (i in 1:5){
  var <- RiskFactors[i]
  Summary[3,(i)] <- sum(Input[,var])
  Summary[4,(i)] <- 100*sum(Input[,var])/length(Input[,var])  
  colnames(Summary) <- paste0(RiskFactors,".Summary")
}   
Summary
```

#Analysis of Catagorical Data
#Summarize Not_OPTIMAL
```{r}
Input <- Not_OPTIMAL

for (i in 1:5){
  var <- RiskFactors[i]
  Summary[5,(i)] <- sum(Input[,var])
  Summary[6,(i)] <- 100*sum(Input[,var])/length(Input[,var])  
  colnames(Summary) <- paste0(RiskFactors,".Summary")
}   
```

#Analysis of Catagorical Data
#Comparison of OPTIMAL and Not OPTIMAL

#Make a Function that Makes a 2x2 Table#
```{r}
#Format of Table 
#     Disease+ Disease-  Total
# Test+ TP        FP      a+c
# Test- FN        TN      b+d
#   a+b       c+d     a+b+c+d

#Make a Function to Calculate Table Statistics#
Table <- function(Diagnosis,Test){
  Input$TP <- ifelse(Test+Diagnosis=="2",1,0)
  TP <- sum(Input$TP)
  Input$TN <- ifelse(Test+Diagnosis=="0",1,0)
  TN <- sum(Input$TN)
  Input$FP <- ifelse(Test-Diagnosis=="1",1,0)
  FP <- sum(Input$FP)
  Input$FN <- ifelse(Test-Diagnosis<0,1,0)
  FN <- sum(Input$FN)
  Output <- matrix(data = NA, nrow =  4, ncol = 1, dimnames=list(c("TP","FP","FN","TN"), c(1)))
  Output[c(1),] <- c(TP)
  Output[c(2),] <- c(FP)
  Output[c(3),] <- c(FN)
  Output[c(4),] <- c(TN)
  return(Output)
}
```

#Make a Function that Calculates Statistics for a 2x2 Table#
```{r}
TableStats <- function(Diagnosis,Test){
  Input$TP <- ifelse(Test+Diagnosis=="2",1,0)
  TP <- sum(Input$TP)
  Input$TN <- ifelse(Test+Diagnosis=="0",1,0)
  TN <- sum(Input$TN)
  Input$FP <- ifelse(Test-Diagnosis=="1",1,0)
  FP <- sum(Input$FP)
  Input$FN <- ifelse(Test-Diagnosis<0,1,0)
  FN <- sum(Input$FN)
  Total <- length(Diagnosis)
  Fishertest<-fisher.test(matrix(c(TP,FP,FN,TN),nrow=2),or=1)
  Output <- matrix(data = NA, nrow =  10, ncol = 1, dimnames=list(c("Outcome+","Outcome+Cat+","Percent","Outcome-","Outcome-Cat+", "Percent","Fisher OR estimate","lower CI", "upper CI","p-value"), c(1)))
  Output[c(1),] <- c(TP)+c(FN)
  Output[c(2),] <- c(TP)
  Output[c(3),] <- c(TP)/(c(TP)+c(FN))
  Output[c(4),] <- c(FP)+c(TN)
  Output[c(5),] <- c(FP)
  Output[c(6),] <- c(FP)/(c(FP)+c(TN))
  Output[c(7),] <- as.numeric(Fishertest$estimate)
  Output[c(8),] <- Fishertest$conf.int[1]
  Output[c(9),] <- Fishertest$conf.int[2]
  Output[c(10),] <- Fishertest$p.value
  return(Output)
}
```

```{r}
Input<-ALL_Cat

for (i in 1:5){
  var <- RiskFactors[i]
  Stats <- TableStats(Input$OPTIMAL,Input[,var])
  pvalue <- Stats[10,1]
  Summary[7,(i)] <- pvalue
}  

Summary
```

#Make an Output Table for the Catagorical Data
```{r}
Output <- t(Summary)
write.table(Output, file="ALL_Cat_ByOptimal.txt", sep="\t", quote=F, row.names=T)
```

#Make a Small Tables Summarizing Ethnicity, Race, and Insurance Subgroupings
#Start with Ethnicity
```{r}
colnames(ALL_Cat)

OPTIMAL_Count <- ALL_Cat %>% group_by(OPTIMAL) %>% select(UCSF_MRN) %>% summarise_each(funs(Count=n()))

Ethnic_Group_TABLE <- ALL_Cat %>% group_by(OPTIMAL, Ethnic_Group) %>% select(UCSF_MRN) %>% summarise_each(funs(Count=n()))
Ethnic_Group_TABLE <- as.data.frame(Ethnic_Group_TABLE)

Ethnicity_Summary <- matrix(data=NA, nrow=3, ncol=4,dimnames=list(c("Hispanic or Latino","Not Hispanic or Latino","Other"),c("OPTIMAL-Count","OPTIMAL-Percent","Not_OPTIMAL-Count","NotOPTIMAL-Percent")))

Ethnicity_Summary[1:3,1] <- Ethnic_Group_TABLE[4:6,3]
Ethnicity_Summary[1:3,3] <- Ethnic_Group_TABLE[1:3,3]
Ethnicity_Summary[1:3,2] <- Ethnicity_Summary[1:3,1]/238
Ethnicity_Summary[1:3,4] <- Ethnicity_Summary[1:3,3]/912

write.table(Ethnicity_Summary, file="Ethnicity_Summary.txt", sep="\t", quote=F, row.names=T)
```

#Make table for Race Subgroups
```{r}
Race_TABLE <- ALL_Cat %>% group_by(OPTIMAL, Race) %>% select(UCSF_MRN) %>% summarise_each(funs(Count=n()))
Race_TABLE <- as.data.frame(Race_TABLE)

Race_Summary <- matrix(data=NA, nrow=7, ncol=4,dimnames=list(c("American Indian", "Asian","Black","Native Hawaiian","Other","Unknown","White"),c("OPTIMAL-Count","OPTIMAL-Percent","Not_OPTIMAL-Count","NotOPTIMAL-Percent")))

Race_Summary[1:7,1] <- Race_TABLE[8:14,3]
Race_Summary[1:7,3] <- Race_TABLE[1:7,3]
Race_Summary[1:7,2] <- Race_Summary[1:7,1]/238
Race_Summary[1:7,4] <- Race_Summary[1:7,3]/912

write.table(Race_Summary, file="Race_Summary.txt", sep="\t", quote=F, row.names=T)
```

#Make table for Insurance Subgroups
```{r}
Insurance_TABLE <- ALL_Cat %>% group_by(OPTIMAL, InsuranceType) %>% select(UCSF_MRN) %>% summarise_each(funs(Count=n()))
Insurance_TABLE <- as.data.frame(Insurance_TABLE)

Insurance_Summary <- matrix(data=NA, nrow=4, ncol=4,dimnames=list(c("Commercial","Medi-Cal","Medicare","Other"),c("OPTIMAL-Count","OPTIMAL-Percent","Not_OPTIMAL-Count","NotOPTIMAL-Percent")))

Insurance_Summary[1:4,1] <- Insurance_TABLE[5:8,3]
Insurance_Summary[1:4,3] <- Insurance_TABLE[1:4,3]
Insurance_Summary[1:4,2] <- Insurance_Summary[1:4,1]/238
Insurance_Summary[1:4,4] <- Insurance_Summary[1:4,3]/912

write.table(Insurance_Summary, file="Insurance_Summary.txt", sep="\t", quote=F, row.names=T)
```

#Make a Small Table Summarizing Discharge Location
```{r}
colnames(ALL_Cat)
library(dplyr)

DischargeLoc_TABLE <- ALL_Cat %>% dplyr::count(ALL_Cat$OPTIMAL, ALL_Cat$Discharge_Disposition)

levels(ALL_Cat$Discharge_Disposition)

DischargeLoc_TABLE <- as.data.frame(DischargeLoc_TABLE)
```

#Do a Wilcox Test to Compare discharge location
```{r}
Input$Discharge_Home <- ifelse(Input$Discharge_Disposition=="Home_or_Self_Care",1, ifelse(Input$Discharge_Disposition=="Home_Health_Care",1,0))

TableStats(Input$OPTIMAL,Input$Discharge_Home)
```

